The \dealii Library, Version 9.1

### 2019-06-05 9.1/paper.tex
some minor changes

\marginpar{I'm sure we have new interfaces. HDF5 and the various AD/SD
  libraries come to mind. Please update.}
\dealii can interface with many other libraries:
\begin{multicols}{3}
\begin{itemize}
\item ADOL-C \cite{Griewank1996a,adol-c}
\item ARPACK \cite{arpack}
\item Assimp \cite{assimp}
\item BLAS and LAPACK \cite{lapack}
\item cuSOLVER \cite{cusolver}
\item cuSPARSE \cite{cusparse}
\item Gmsh \cite{geuzaine2009gmsh}
\item GSL \cite{gsl2016}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item nanoflann \cite{nanoflann}
\item NetCDF \cite{rew1990netcdf}
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{Burstedde2018,p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item ROL \cite{ridzal2014rapid}
\item ScaLAPACK \cite{slug}
\item SLEPc \cite{Hernandez:2005:SSF}
\item SUNDIALS \cite{sundials}
\item TBB \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.

@@

\dealii is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people contributed code to
this release:\\
%
% get this from the changes/*/* files using the command listed in the
% release-tasks paper and remove the authors of this paper
%
% updated 5/12/2019
\marginpar{Remove all other authors of this paper}
\marginpar{Do we want to spell out who the Gingko devs are?}
  Giovanni Alzetta,
  Mathias Anselmann,
  Daniel Appel,
  Alexander Blank,
  Vishal Boddu,
  Benjamin Brands,
  Pi-Yueh Chuang,
  T. Conrad Clevenger,
  Sambit Das,
  the Ginkgo developers,
  Stefano Dominici,
  Nivesh Dommaraju,
  Niklas Fehn,
  Isuru Fernando,
  Andreas Fink,
  Daniel Garcia-Sanchez,
  Rene Gassm{\"o}ller,
  Alexander Grayver,
  Joshua Hanophy,
  Logan Harbour,
  Graham Harper,
  Daniel Jodlbauer,
  Stefan Kaessmair,
  Eldar Khattatov,
  Alexander Knieps,
  Uwe K{\"o}cher,
  Kurt Kremitzki,
  Dustin Kumor,
  Ross Kynch,
  Damien Lebrun-Grandie,
  Jonathan Matthews,
  Stefan Meggendorfer,
  Pratik Nayak,
  Lei Qiao,
  Ce Qin,
  Reza Rastak,
  Roland Richter,
  Alberto Sartori,
  Svenja Schoeder,
  Sebastian Stark,
  Antoni Vidal,
  Jiaxin Wang,
  Yuxiang Wang,
  Zhuoran Wang.

>>>>

\marginpar{I'm sure we have new interfaces. HDF5 and the various AD/SD
  libraries come to mind. Please update. MM: The list actually looks pretty
  complete (I have not verified that we actually cite *all* canonical
  publications for a given library).}
\dealii can interface with many other libraries:
\begin{multicols}{3}
\begin{itemize}
\item ADOL-C \cite{Griewank1996a,adol-c}
\item ARPACK \cite{arpack}
\item Assimp \cite{assimp}
\item BLAS and LAPACK \cite{lapack}
\item cuSOLVER \cite{cusolver}
\item cuSPARSE \cite{cusparse}
\item Gmsh \cite{geuzaine2009gmsh}
\item GSL \cite{gsl2016}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item nanoflann \cite{nanoflann}
\item NetCDF \cite{rew1990netcdf}
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{Burstedde2018,p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item ROL \cite{ridzal2014rapid}
\item ScaLAPACK \cite{slug}
\item SLEPc \cite{Hernandez:2005:SSF}
\item SUNDIALS \cite{sundials}
\item TBB \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.

@@

\dealii is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
% updated 6/05/2019
  Giovanni Alzetta,
  Mathias Anselmann,
  Daniel Appel,
  Alexander Blank,
  Vishal Boddu,
  Benjamin Brands,
  Pi-Yueh Chuang,
  T. Conrad Clevenger,
  Sambit Das,
  Stefano Dominici,
  Nivesh Dommaraju,
  Niklas Fehn,
  Isuru Fernando,
  Andreas Fink,
  Daniel Garcia-Sanchez,
  Rene Gassm{\"o}ller,
  Alexander Grayver,
  Joshua Hanophy,
  Logan Harbour,
  Daniel Jodlbauer,
  Stefan Kaessmair,
  Eldar Khattatov,
  Alexander Knieps,
  Uwe K{\"o}cher,
  Kurt Kremitzki,
  Dustin Kumor,
  Damien Lebrun-Grandie,
  Jonathan Matthews,
  Stefan Meggendorfer,
  Pratik Nayak,
  Lei Qiao,
  Ce Qin,
  Reza Rastak,
  Roland Richter,
  Alberto Sartori,
  Svenja Schoeder,
  Sebastian Stark,
  Antoni Vidal,
  Jiaxin Wang,
  Yuxiang Wang,
  Zhuoran Wang.
